Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-12 paper/main.tex
Added names and date to Preface
Added abstract

@@

Lastly, the Open Source community behind Tahoe-LAFS deserves credit for the
immense amount of hours they put on an awesome project, and Thomas Pornin for
providing a working copy of his library of implementations, which saved us a lot
of work.

>>>>

Most of the cloud applications today are highly dependant on the use of
cryptographic hash functions. The distributed file system Tahoe-LAFS is no
exception, and uses hashing algorithms extensively for verification of the
integrity of its files.

In light of the ongoing NIST competition for selecting the new, standard
cryptographic hash function named SHA-3, we tried out the 14 second
round candidates in the Tahoe-LAFS file system using automated tests to measure
the performance differences. Only the immutable file support was tested.

Since the Tahoe-LAFS is programmed in Python, we had to make bindings to the
SHA-3 implementations written in C, before making the necessary changes to the
Tahoe-LAFS code. Several tasks where automated using scripts, to avoid doing
manual work of distributing changes to the test grid.

In general, four of the candidates perform better than the currently used
SHA-256 -- BLAKE, BlueMidnightWish, Shabal and Simd.
By utilizing the performance improvements given by SHA-3, Tahoe-LAFS could
save $5\%$ on upload operations by changing hashing function to the best
performing candidate.

The benchmarking tool SUPERCOP measures performance and drives the development
forwards for the SHA-3 candidates, but we argue that since the SUPERCOP API does
not conform with the NIST SHA-3 API, vital functionality are left out, making
integration and testing with existing software hard.

@@

Lastly, the Open Source community behind Tahoe-LAFS deserves credit for the
immense amount of hours they put on an awesome project, and Thomas Pornin for
providing a working copy of his library of implementations, which saved us a lot
of work.
\vspace{13pt}

Best regards,

\begin{center}
Eirik Haver and Pål Ruud
\vspace{13pt}

December 16, 2010
\end{center}
